### 2019-10-15 tesis_hiram/Chapter4/chapter4.tex
algo

	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation for higher luminosities}
	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9fb $^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150fb $^{-1}$ for run 2 finished in 2018. Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb . Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same
	\pagebreak

@@

	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1. But even with the increase of number of events, the ratio of signal and data is still very small, with a slightly increase in the ratio in the 3000 fb $^{-1}$ case.  In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit. \\

@@

	\begin{table}[ht!]
		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			Luminosity (fb $^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
			\hline
			35.9 & 1.00 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
			\hline
			150& 1.00 $\pm$  6.7& 10.7  &  1.0 $\pm$  0.4 &1.8\\
			\hline
			300&1.00 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
			\hline
			3000&1.00 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
			\hline
		\end{tabular}
		\label{upper}
	\end{table}

@@

	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$ and increase the signal data ratio . 
	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data. This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater. For 3000 fb$^{-1}$ the uncertainty on mu is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.

>>>>

	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation for higher luminosities}
	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9fb $^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150fb $^{-1}$ for run 2 finished in 2018. Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb . Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same.
	\\

	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1. But even with the increase of number of events, the ratio of signal and data is still very small.  In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit. 
	\pagebreak

@@

@@

	\begin{table}[ht!]
		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			Luminosity (fb $^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
			\hline
			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
			\hline
			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
			\hline
			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
			\hline
			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
			\hline
		\end{tabular}
		\label{upper}
	\end{table}

@@

	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$. 
	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data. This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater. For 3000 fb$^{-1}$ the uncertainty on mu is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.
